---
title: "UFO_sightings:Project 1"
author: "Priti Rayamajhi"
output: 
  html_document: default
  pdf_document: default
  word_document: default
---
```{r setup, include=FALSE}
 knitr::opts_chunk$set(echo = TRUE)
```


## Context/Content : Data set is from Kaggle - https://www.kaggle.com/NUFORC/ufo-sightings

Dataset represents unidentifed flying objects reports in the last century. We are using the scrubbed dataset that is available from Kaggle. There was also a complete dataset, but lacked information for some of the entries. The dataset includes 80,332 rows of observations with 11 columns. The columns are divided by date, time, city, state, country, shape, description, and duration of each sighting. 

## Questions: 
- Is there a correlation between time and shape? (Is there a significance when the sighting is seen and the shape of the UFO?) 
- Are certain shapes of the UFO more frequent in different countries and states in the US? 

```{r}
# all the packages that I ran 
library(tidyverse)
library(dplyr)
library(ggplot2)
library(lubridate)
library(tidyr)
library(readr)
```


```{r}
UFO_sightings <- read_csv("scrubbed.csv")
```

```{r}
# Structure of data

str(UFO_sightings)
head(UFO_sightings)
tail(UFO_sightings)
```

# - Is there a significance when the sighting is seen and the shape of the UFO? (correlation between time and shape?)

```{r}
# Using the lubridate package, I wanted to turn the column "datetime" into date and time. This will make comaparing the shape with time easier since R can read the column as a date and time versus as a character like it was before.

# This changes the "datetime" format from a character to read as date 

UFO_new <- mutate(UFO_sightings, datetime = mdy_hm(UFO_sightings$datetime))

# Added year and month columns separate from date into the dataset to be able to sort through quickly. 

UFO_new <- mutate(UFO_new, year = year(datetime))
UFO_new <- mutate(UFO_new, month = month(datetime, label = TRUE))

UFO_new

# looked at the patterns of the year to see what the sightings looked like annually in order to copare that to the shape 

ggplot(data = UFO_new, mapping = aes(x = year)) + geom_freqpoly(bins = 1000) + ggtitle("Annual UFO Sightings Reported Worldwide")

# The result show that as we get closer to the late 1900's and 2000's we see more sightings being reported. This might be due to many factors like technology or the population of the locations reporting more frequently than other locations. 

```
```{r}
Shape <- UFO_new[, "shape"]

UFO_wo_shapes <- filter(UFO_new, shape!= c("other"))
 # took out other in shapes 

most_frequent_shapes <- names(sort(table(UFO_wo_shapes$shape),decreasing = TRUE)[1:10])
most_frequent_shapes

# most frequent shapes in the dataset

ggplot(data = UFO_wo_shapes, mapping = aes(x=shape, y= 100)) + geom_bar( stat = "identity", fill="Pink") + labs( y= "Count", x= "shape") + ggtitle("Shapes of UFO Sightings")

```
```{r}
ggplot(data = UFO_new, mapping = aes(x= year, y = shape)) + geom_bar( stat = "identity", fill="Pink") + labs( y= "Count", x= "Years") + ggtitle("Most Frequent Shapes of UFO Sightings each Year")
```


#- Are certain shapes of the UFO more frequent in different countries? States in the US?
```{r}
usa <- filter(UFO_sightings, country=="us")
plot(usa$shape, xlab="Shape", ylab="Number of Sightings", main="Prevalent UFO Shapes in the USA")

ggplot(data = usa, mapping = aes(x= year, y = shape)) + geom_histogram(mapping = aes(x = year, y = shape, fill = "blue")) + ggtitle("Reported UFO Sightings in United States by Month and Year")


canada <- filter(UFO_sightings, country=="ca")
plot(canada$shape, xlab="Shape", ylab="Number of Sightings", main="Prevalent UFO Shapes in the Canada")

au <- filter(UFO_sightings, country=="au")
plot(au$shape, xlab="Shape", ylab="Number of Sightings", main="Prevalent UFO Shapes in the Australia")

gb <- filter(UFO_sightings, country=="ca")
plot(gb$shape, xlab="Shape", ylab="Number of Sightings", main="Prevalent UFO Shapes in the Great Britian")

```
# 
```{r}
usa <- filter(UFO_sightings, country=="us")
us_state <- usa[, "state"]
us_state

summary(us_state)
plot(us_state, xlab="States", ylab="Sightings", main="Sightings in US States")
```




